Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Good and Bad for Pollster
Good and Bad for Pollster

>>>>

The questionnaire is well-designed, with a collaborative approach that reduces respondent burden and improves comprehension. A thoughtfully structured skip pattern enhances flow and minimizes dropout rates. The probability-based sampling, combined with extensive weighting and stratification, enables a representative sample of adults. However, heavy reliance on web-based responses may introduce Internet bias, potentially underrepresenting non-Internet households. Additionally, the questionnaire’s complexity may increase participant fatigue, affecting response completeness. The response rate of approximately 47.4% also indicates some level of attrition in the sample.
